Checking Big Suffix and LCP Arrays by Probabilistic Methods

### 2017-06-06 camera-ready/TC-2016-10-0714.tex
2017/06/06

\author{
	Yi~Wu,
	Ge~Nong,
	Wai~Hong~Chan,
	Ling~Bo~Han% <-this % stops a space
	\IEEEcompsocitemizethanks{
		\IEEEcompsocthanksitem Y. Wu, G. Nong (corresponding author) and L.~B.~Han are with the Department of Computer Science, Sun Yat-sen University, Guangzhou, and the SYSU-CMU Shunde International Joint Research Institute, Shunde, China. E-mails: wu.yi.christian@gmail.com, issng@mail.sysu.edu.cn, hanlb@mail2.sysu.edu.cn.

		\IEEEcompsocthanksitem Wai Hong Chan (corresponding author) is with the Department of Mathematics and Information Technology, The Education University of Hong Kong, Hong Kong. E-mail: waihchan@ied.edu.hk.
}}% <-this % stops a space

@@

	\includegraphics[width = 0.9\columnwidth]{example}
	\caption{An example for computing and comparing fingerprints for substrings specified by the LCP-values of neighboring suffixes in $sa$. \label{fig:example}}	
\end{figure}

@@

%\section*{Acknowledgment}
%The work of Y. Wu, G. Nong and L. B. Han were supported by the Guangzhou Science and Technology Program grant 201707010165 and the Project of DEGP grant 2014KTSCX007. {\color{red} %The work of W. H. Chan was supported by...}

@@

>>>>

\author{
	Yi~Wu,
	Ge~Nong,~\IEEEmembership{Senior~Member,~IEEE},
	Wai~Hong~Chan,
	Ling~Bo~Han% <-this % stops a space
	\IEEEcompsocitemizethanks{
		\IEEEcompsocthanksitem Y. Wu and G. Nong (corresponding author) are with the Department of Computer Science, Sun Yat-sen University, Guangzhou, and the SYSU-CMU Shunde International Joint Research Institute, Shunde, China. E-mails: wu.yi.christian@gmail.com, issng@mail.sysu.edu.cn.

		\IEEEcompsocthanksitem Wai Hong Chan (corresponding author) is with the Department of Mathematics and Information Technology, The Education University of Hong Kong, Hong Kong. E-mail: waihchan@ied.edu.hk.

		\IEEEcompsocthanksitem L.~B.~Han is with the Key Laboratory of Machine Intelligence and Advanced Computing (Sun Yat-sen University), Ministry of Education, China, E-mail: hanlb@mail2.sysu.edu.cn.		
}}% <-this % stops a space

@@

	\includegraphics[width = 0.9\columnwidth]{example.eps}
	\caption{An example for computing and comparing fingerprints for substrings specified by the LCP-values of neighboring suffixes in $sa$. \label{fig:example}}	
\end{figure}

@@

\section*{Acknowledgment}
The work of G. Nong was supported by the Guangzhou Science and Technology Program grant 201707010165 and the Project of DEGP grant 2014KTSCX007. The work of W. H. Chan was supported by GRF (810012), Research Grant Council, Hong Kong SAR.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{ywu_avator.eps}}]{Yi Wu}
received his BSc and MSc degrees in computer science from the Central-South University in 2009 and the Sun Yat-sen University in 2012, both in China, respectively. He is now pursuing a Ph.D. degree in computer science at the Sun Yat-sen University, China. His current research interests are switching and routing, and string processing for massive data.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gnong_avatar.eps}}]{Ge Nong}
received his B.E. and M.E. degrees, both in Computer Engineering, from the NanJing University of Aeronautics and Astronautics in 1992 and the South China University of Science and Technology in 1995, respectively. He received the Ph.D. in Computer Science from the Hong Kong University of Science and Technology in 1999. Then, he joined STMicroelectronics as a senior researcher with R\&D on IC and system technologies for high-speed switches and routers. He is now a Professor in the Department of Computer Science of Sun Yat-sen University in Guangzhou, China. His current research interests include algorithms, computer and communication networks, switching theory and performance evaluation.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{chan_avatar.eps}}]{Wai Hong Chan}
received the BSc, MPhil and Ph.D. in Mathematical Science from the Hong Kong Baptist University, Hong Kong Special Administrative Region, China, in 1994, 1996 and 2003 respectively. He joined the Department of Mathematics and Information Technology of the Education University of Hong Kong in 2011, and now the Head of Department. His current research interests include algorithm design, quantum information, graph theory and combinatorics.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{lbhan_avatar.eps}}]{Ling Bo Han}
received his B.S. degree in Computer Science from the Taiyuan Normal University in 2006 and the M.S. degree in Computer Science from the Guangxi Normal University in 2009, both in China. He is now pursuing a Ph.D. degree in the School of Data and Computer Science at the Sun Yat-sen University, China. His current research interests are data mining, and string processing for massive data.
\end{IEEEbiography}
